### 2019-11-04 thesis/txt/5-study.tex
restart study chapter

\chapter{Empirical Comparison Study}
\label{sec:study}
To investigate how different factors \todo{do we list these somewhere?} influence BLIRTs we evaluate the three techniques implemented in our tool on the \emph{Failing Build Log Data Set}.

\begin{figure}[htbp]
	\centering
	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Process of our technique comparison study}
	\label{fig:study}
\end{figure}

\section{Study Design}
\bp{We compare three different techniques: PBE, TS, SKWS (itemize and link to their explanation?) and as a baseline: random line rerieval (RLR): retrieves random lines from the build log, (describe in chapper about BLIRTs??), number of lines: average of output lines from past}
We configure the technique for every example set with an increasing count of I/O examples and then run the retrieval on the next I/O example, the \emph{test I/O example}.
The output from the test I/O example is the oracle for our evaluation.
The examples are sorted and selected chronologically, i.e. the technique is configured with examples from the directly preceeding build logs to extract information from the test log.
The extraction quality of a BLIRT run is evaluated on only one build log, as it should be suitable for every coming example.
Especially the one directly succeeding the configuration.
If the information retrieval there is bad, we expect the user to directly change the configuration again or be dissapointed with his selection of technique.

When evaluating a BLIRT run we measure the following data points:
\begin{itemize}
	\item \textbf{Successful} A BLIRT run is successful when the retrieved output contains all the lines the oracle output.
	\item \textbf{Accuracy} \todo{currently: levenstein difference of input and output, maybe: change to false pos and neg lines}
	\item \textbf{Proximity} \todo{No! let's do that with "}
\end{itemize}

taking The Failing Build Log Data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?

\section{Results}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
	\label{fig:categories-dataset}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
		\caption{Distribution of the Count of Categories within the Examples used for Configuration in our Study}
		\label{fig:categorycount-examplecount-dataset}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{caption}
		\label{fig:xxxy}
	\end{minipage}
\end{figure}

\subsection{Category Distribution in Data Set}
Categories distributed in over data set
- why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
- Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
- Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.

\subsection{Regular Expression Program Synthesis by Example (PBE)}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
		\caption{Successful Extractions per Number of Examples for PBE}
		\label{fig:success-examples-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
		\caption{Precision of Extractions per Number of Examples for PBE}
		\label{fig:precision-pbe}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
		\caption{Precision of PBE Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-pbe}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Reasons for PBE Runs to Fail}
		\label{fig:failure-reason-pbe}
	\end{minipage}
\end{figure}

This section addresses the results produced by the PBE technique in our study.
We start by comparing success rate and precision for different example counts and showing the influence of example categories.
Next we go into detail in which cases pbe fails
\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}
\subsubsection{Specific Failure Reasons}
\todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
% \subsection{Successful Extractions}
% successful is interpreted by us as: all lines that were desired (within our oracle) were also extracted during the test

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
		\caption{Successful Extractions per Number of Examples for TS}
		\label{fig:success-examples-ts}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
		\caption{Precision of Extractions per Number of Examples for TS}
		\label{fig:precision-ts}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
		\caption{Precision of TS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-ts}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
		\caption{Successful Extractions per Number of Examples for SKWS}
		\label{fig:success-examples-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
		\caption{Precision of Extractions per Number of Examples for SKWS}
		\label{fig:precision-skws}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
		\caption{Precision of SKWS Extractions by CategoryCount}
		\label{fig:precision-categorycount-examplecount-skws}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}

@@

\subsection{Comparing All Techniques}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
		\caption{Successful Extractions for all Techniques Compared}
		\label{fig:success-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
		\caption{Precision of Extractions for all Techniques Compared}
		\label{fig:precision-all}
	\end{minipage}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
		\caption{\todo{todo}}
		\label{fig:precision-category-singularity-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
		\caption{\todo{todo}}
		\label{fig:single-cateogry-precision-all}
	\end{minipage}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
		\caption{\todo{todo}}
		\label{fig:precision-categorycount-examplecount-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{\todo{todo}}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsubsection{Success-Rate}
\subsubsection{Precision}
\subsubsection{Example Categories}

\section{Discussion}
\todo{draw decision tree}

interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
\section{Threats to Validity}

>>>>

\chapter{Empirical Comparison Study}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{Failing Build Log Data Set}.
This chapter describes our study design, the analysis of the study results and threats to the validity of our conclusions.
The analysis of the study results first focusses on each of the three techniques and describes how each one performs best.
Later we compare them against each other and describe their trade offs against each other.
This chapter answers our second research question and its subquestions:
\begin{simplebox}{Research Questions}
\begin{itemize}
  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}
\end{simplebox}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/study-design.pdf}
	\caption{Study Design of our technique comparison study}
	\label{fig:study}
\end{figure}

\section{Study Design}
For the comparison study we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections \ref{sec:expl-pbe},\ref{sec:expl-ts} and \ref{sec:expl-skws}.
RLR, explained in Section \ref{sec:expl-rlr}, acts as a baseline for the comparison.
We run four techniques on the example sets from the \emph{Failing Build Log Data Set}.

The examples are sorted chronologically, i.e. a technique is configured with examples from the directly preceding build logs.
For each example set and each technique, we select one to five successive I/O examples as configuration, the \emph{configuring I/O examples}, and run the chunk retrieval on the next I/O example, the \emph{test I/O example}.

For each of our evaluation runs we measure the desired vs. actual output lines of the chunk retrieval.
The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
From this we obtain true/false positives/negatives and calculate precision, recall and accuracy, which we use to answer \textbf{RQ2.2}.
We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.

%taking The Failing Build Log Data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?

\section{Analysis}
This section presents the evaluation results for PBE, CTS and KWS separately and discusses under which circumstances these techniques yield best results.
Afterwards it compares the three techniques with each other and RLR as baseline.
The section concludes with recommendations on which technique is suited for different situations.

% \begin{figure}[htbp]
% 	\centering
% 	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
% 	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
% 	\label{fig:categories-dataset}
% \end{figure}

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
% 		\caption{Distribution of the Count of Categories within the Examples used for Configuration in our Study}
% 		\label{fig:categorycount-examplecount-dataset}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{caption}
% 		\label{fig:xxxy}
% 	\end{minipage}
% \end{figure}

% \subsection{Category Distribution in Data Set}
% Categories distributed in over data set
% - why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
% - Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
% - Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Success of Chunk Retrieval Runs with PBE}
		\label{fig:failure-reason-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Success of Chunk Retrieval Runs with PBE Compared with Category Count}
		\label{fig:failure-reason-categorycount-PBE}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision of PBE Chunk Retrieval Results Compared with Example Count}
		\label{fig:precision-extraction-result-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-singlecategory-swarm-PBE.pdf}
		\caption{Precision of PBE Chunk Retrieval Compare with Example Count and Category Singularity}
		\label{fig:precision-singlecategory-swarm-PBE}
	\end{minipage}
\end{figure}
\subsection{Regular Expression Program Synthesis by Example (PBE)}
Out of the 400 runs in our evaluation, 5 runs per each of the 80 example sets, PBE extracted all the desired lines in 138 cases.
Figure \ref{fig:failure-reason-PBE} shows that in 89 cases a program was successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring examples.

Figure \ref{fig:failure-reason-categorycount-PBE} shows that the success of the program syntesis algorithm highly depends on the structural categories present in the configuring examples.
Programs could only be synthesized if at maximum two categories were present.

More than three examples yield no improvement in the precision of PBE chunk retrieval, as you can see in Figures \ref{fig:precision-extraction-result-PBE} and \ref{fig:precision-singlecategory-swarm-PBE}.

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
% 		\caption{Successful Extractions per Number of Examples for PBE}
% 		\label{fig:success-examples-pbe}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
% 		\caption{Precision of Extractions per Number of Examples for PBE}
% 		\label{fig:precision-pbe}
% 	\end{minipage}
% \end{figure}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
% 		\caption{Precision of PBE Extractions by CategoryCount}
% 		\label{fig:precision-categorycount-examplecount-pbe}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
% 		\caption{Reasons for PBE Runs to Fail}
% 		\label{fig:failure-reason-pbe}
% 	\end{minipage}
% \end{figure}

% This section addresses the results produced by the PBE technique in our study.
% We start by comparing success rate and precision for different example counts and showing the influence of example categories.
% Next we go into detail in which cases pbe fails
% \subsubsection{Success-Rate}
% \subsubsection{Precision}
% \subsubsection{Example Categories}
% \subsubsection{Specific Failure Reasons}
% \todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
% \subsection{Successful Extractions}
% successful is interpreted by us as: all lines that were desired (within our oracle) were also extracted during the test

@@

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
% 		\caption{Successful Extractions per Number of Examples for TS}
% 		\label{fig:success-examples-ts}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
% 		\caption{Precision of Extractions per Number of Examples for TS}
% 		\label{fig:precision-ts}
% 	\end{minipage}
% \end{figure}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
% 		\caption{Precision of TS Extractions by CategoryCount}
% 		\label{fig:precision-categorycount-examplecount-ts}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{xxx}
% 		\label{fig:xxx}
% 	\end{minipage}
% \end{figure}

@@

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
% 		\caption{Successful Extractions per Number of Examples for SKWS}
% 		\label{fig:success-examples-skws}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
% 		\caption{Precision of Extractions per Number of Examples for SKWS}
% 		\label{fig:precision-skws}
% 	\end{minipage}
% \end{figure}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
% 		\caption{Precision of SKWS Extractions by CategoryCount}
% 		\label{fig:precision-categorycount-examplecount-skws}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{xxx}
% 		\label{fig:xxx}
% 	\end{minipage}
% \end{figure}

@@

\subsection{Comparing All Techniques}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
% 		\caption{Successful Extractions for all Techniques Compared}
% 		\label{fig:success-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
% 		\caption{Precision of Extractions for all Techniques Compared}
% 		\label{fig:precision-all}
% 	\end{minipage}
% \end{figure}

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:precision-category-singularity-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:single-cateogry-precision-all}
% 	\end{minipage}
% \end{figure}

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:precision-categorycount-examplecount-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:xxx}
% 	\end{minipage}
% \end{figure}

% \section{Discussion}
% \todo{draw decision tree}

% interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
\section{Threats to Validity}
%chronologically selected examples -> very specific view
